\documentclass[10pt,a4paper]{article}

% Packages
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}

% Colors
\definecolor{linkblue}{RGB}{0,102,204}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
}

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% Remove page numbers
\pagenumbering{gobble}

% Custom commands
\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\resumeSubheading}[4]{
    \item[]
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-4pt}
}

\begin{document}

%----------HEADER----------
\begin{center}
    {\LARGE \textbf{Kyungho Byoun}} \\[6pt]
    \faEnvelope\ \href{mailto:kyungho.byoun@gmail.com}{kyungho.byoun@gmail.com} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/kyungho-byoun/}{linkedin.com/in/kyungho-byoun} \quad
    \faGithub\ \href{https://github.com/Byunk}
{github.com/Byunk}
\end{center}

\vspace{-4pt}
\begin{center}
    \textit{Software developer expertise in large scale data engineering. Passionate about building data-driven products from 0 to 1.}
\end{center}

%----------EXPERIENCE----------
\section{Experience}
\begin{itemize}[leftmargin=0pt, label={}]
    \resumeSubheading
        {Software Developer}{Apr 2024 -- Present}
        {SAP}{Seoul, South Korea}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Architected and implemented a petabyte-scale observability microservice aggregating telemetry from \textbf{60} global regions and \textbf{375} Kubernetes clusters into a unified Delta Lake using Spark and HANA Data Lake Files.
        \item Designed end-to-end data pipelines serving worldwide teams with 30+ tables and growing, enabling previously impossible analyses such as Major Upgrade Window downtime tracking across pod lifecycle events.
        \item Built an LLM-powered analytics chatbot with RAG for natural language querying of observability data. Achieved \textbf{41.6}\% accuracy on complex internal NL-to-SQL benchmarks tailored to business context.
    \end{itemize}

    \resumeSubheading
        {Intern}{Jul 2023 -- Apr 2024}
        {SAP}{Seoul, South Korea}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Designed and implemented a PoC using Istio service mesh to enable local-remote cluster integration. Submitted for US patent as the primary contributor.
        \item Built an automated testing framework that for HANA DB, identifying \textbf{11} bugs in production versions.
    \end{itemize}

    \resumeSubheading
        {Undergraduate Researcher}{Jul 2022 -- Jun 2023}
        {KAIST Augmented Reality Research Center}{Daejeon, South Korea}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Designed and implemented a 5-stage sleep estimation algorithm for smart mattress integration using digital signal processing in MATLAB and Python.
        \item Iterated through testing with 5 participants from Kyung Dong Navien; achieved only \textbf{5.61}\% difference compared to Galaxy Watch (ECG-based) benchmark.
    \end{itemize}
\end{itemize}

%----------EDUCATION----------
\section{Education}
\begin{itemize}[leftmargin=0pt, label={}]
    \resumeSubheading
        {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, South Korea}
        {Bachelor of Engineering in Computer Science, Aerospace Engineering}{Mar 2017 -- Feb 2024}
\end{itemize}

%----------PROJECTS----------
\section{Projects}
\begin{itemize}[leftmargin=0pt, label={}]
    \resumeSubheading
        {\href{https://www.branchy.io/}{branchy.io}}{Ongoing}
        {Side Project}{}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Building an ideation platform that visualizes ideas in graph with LLM-powered understanding and enhancement.
    \end{itemize}
    
    \resumeSubheading
        {\href{https://drive.google.com/file/d/1E7P0ng33f29_aVWq5d71I94I23YkFpmM/view?pli=1}{NASA Space Apps Challenge}}{2025}
        {Honorable Mention}{}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Developed risk analysis of Korean west/east coast power plants based on SAR dataset.
    \end{itemize}

    \resumeSubheading
        {\href{https://github.com/KAIST-Google-Solution-Challenge}{Google Solution Challenge}}{2023}
        {Global Top 100, Team Lead}{}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Developed a real-time scam detection application using BERT and Google Cloud, aimed at protecting socially disadvantaged individuals.
    \end{itemize}

    \resumeSubheading
        {KAIST App Startup Competition}{Jul 2022 -- Dec 2022}
        {\$\textbf{5,500} Award, Team Lead}{}
    \begin{itemize}[leftmargin=12pt, label=\textbullet, nosep, topsep=4pt]
        \item Proposed solutions and business strategies to address the supply and demand imbalance in the carbon credit market.
    \end{itemize}

    \resumeSubheading
        {Open Source Contributor}{Lifelong}
        {Agno, Langchain, SQL Metadata}
        {}
\end{itemize}

%----------SKILLS----------
\section{Skills}
\begin{itemize}[leftmargin=0pt, label={}, nosep]
    \item[] \textbf{Professional:} Python, Spark, Delta Lake, Kubernetes \quad \textbf{Proficient:} React
\end{itemize}

%----------LANGUAGES----------
\section{Languages}
\begin{itemize}[leftmargin=0pt, label={}, nosep]
    \item[] \textbf{Korean:} Native Proficiency \quad \textbf{English:} Professional Working Proficiency
\end{itemize}

\end{document}
